Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-09-01 papers/thesis-kirstie/thesis.tex
rename to thesis and make it draft mode
comment out graphics from thesis for now

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{plot_HardSphere_Potential.png}
    %\includegraphics[height=3.5cm]{plot_HardSphere_Potential.png}
    %\caption{Hard Sphere Potential}
    \caption{A Hard Sphere Potential is zero for $r>2R$, and infinity for $r\leq{2R}$ which is approximately 1.225 in this example.}
    \label{fig:HardSphere_potential}
  \end{figure}
\[{}\]
\[{}\]
\[{}\]
\[{}\]

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{LJ_Potential.png}
    \caption{Leonard-Jones Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{LJ_Potential_2part.png}
    \caption{Leanard-Jones Potential broken into two parts for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential_2parts}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{WCA_Potential.png}
    \caption{WCA Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:WCA_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
   % \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=3.5cm]{TwoSpheres.png}
    %\end{subfigure} 
    %\begin{subfigure}[b]{0.4\linewidth}
    %  \includegraphics[height=3.5cm]{2spheres.png}
    %\end{subfigure} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure} 
%\[\]

@@

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=4.5cm]{plot_alpha_vs_KbT.png}
      %\includegraphics[height=5cm]{plot_alpha_vs_KbT.png}
      \caption{$\alpha$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=4.5cm]{plot_xi_vs_KbT.png}
      %\includegraphics[height=5cm]{plot_xi_vs_KbT.png}
      \caption{$\Xi$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \caption{These plots, generated with $\sigma=1$ and $\epsilon=1$, show how the parameters $\alpha$ and $\Xi$ vary with temperature. (a) $\alpha$ decreases with increasing temperature. (b) $\Xi$ rapidly increases for temperatures below $\frac{k_BT}{\epsilon}=52$ and then gradually decreases.}
    \label{fig:alphaXivsT}
    \end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{Verf.png}
    %\includegraphics[height=5cm]{Verf.png}
    \caption{Error Function Potential $V_{erf}(r)$ at several temperatures with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ shown in black.}
    \label{fig:erf_potential}
  \end{figure}

@@

  \begin{figure}[h!]
    \centering
    \includegraphics[height=3.5cm]{PrimitiveCellLightBlue.png}
    \caption{The Primivitive Crystal Cell is shown by the shaded parallelpiped}
    \label{fig:primitivecell_firsttime}
  \end{figure}
%-------------------------------

@@

%For each particular temperature, the pressure of the liquid and the solid are the same at the point of transistion. 
\begin{figure}[h!]
    \centering
    \includegraphics[height=5cm]{P-T_Diagram.png}
    \caption{Conceptual Pressure-Temperature Phase Diagram}
    \label{fig:P-T_Diagram}
  \end{figure}
The pressure can be related to the Helmholtz free energy F, which is minimized for a system at fixed temperature, volume and number of particles as the entropy of the system and its surroundings is maximized. The negative of the partial derivative of the Helmholtz free energy with respect to volume V at a fixed temperature T and number of particles N equals the pressure. 
\begin{equation}{P=-\frac{\partial{F}}{\partial{V}}\bigg|_{T,N}}\end{equation}
\noindent Dividing both the Helmholtz free energy and the volume by the number of particles, the partial derivative of the Helmholtz free energy with respect to volume becomes the partial derivative of the Helmholtz free energy per atom with respect to the inverse number density. \begin{equation}{P=-\frac{\partial{\frac{F}{N}}}{\partial{\frac{V}{N}}}\bigg|_{T,N} = -\frac{\partial{f}}{\partial{\frac{1}{n}}}\bigg|_{T,N}}\end{equation} Thus, the pressure corresponds to the slope of the curve on a plot of the Helmholtz free energy per atom versus the inverse density at fixed temperature.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{MDTC.png}
    \caption{Identifying densities at the solid-liquid transition using Maxwell's Double Tangent Construction}
    \label{fig:MaxwellDT}
  \end{figure}

@@

The pressure at the transistion point can be obtained from the point of intersection that occurs when the Gibbs free energy per atom is plotted against the pressure for both the liquid and the solid at fixed temperature, as shown in Figure \ref{fig:GibbsvsP}. These curves are constructed from the slope and cooresponding y-intercept data collected from lines tangent along the curves on the the Helmholtz free energy per atom verses inverse density plots for both the liquid and the solid. 
\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{MDTC-2.png}
    \caption{Pressure is found at point of intersection which occurs when $g_L=g_S$}
    \label{fig:GibbsvsP}
  \end{figure}
%CURVE FITTING! - put in methods/analysis

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{MDTC-3.png}
    \caption{The liquid and solid densities at the point of transistion are found from a plot of pressure vs inverse denisty for both the liquid and the solid.}
    \label{fig:Pvsinvn}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{T-n_Diagram.png}
    \caption{Conceptual Temperature-Density Phase Diagram used to identify the number densities of the liquid and the solid during a phase transistion. The gray region is where the liquid and the solid coexist, and are therefore not pure states.}
    \label{fig:T-n_Diagram}
  \end{figure} 
%One way of implementing this practically is to determine what the Helmholtz free energy would be for both the liquid and solid phases at a particular temperature and density. Whichever phase has the lower Helmholtz free energy will be the phase that the substance will be in. 
%\[\]
\[\]
IC. Classical Density Functional Theory (cDFT)

@@

  \begin{figure}[h!]
    \centering
    \includegraphics[height=4.5cm]{PrimitiveCellLightBlue.png}
    \caption{The Primivitive Crystal Cell is shown by the shaded parallelpiped}
    \label{fig:primitivecell}
  \end{figure}

  \begin{figure}[h!]
    \centering
    \includegraphics[height=4.5cm]{Simple_Cell.png}
    \caption{A Simplified Crystal Cell}
    \label{fig:simplecell}
  \end{figure}

@@

  \begin{figure}[h!]
    \centering
    \includegraphics[height=2.5cm]{Ensemble_Gaussian.png}
    \caption{A Gaussian Distribution Number Density Profile}
    \label{fig:Ensemble_Gaus}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{Gaussian_Plot.png}
    \caption{A 2D Gaussian Distribution of width 2$\sigma$}
    \label{fig:Gaus_plot}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=2.5cm]{Ensemble_Smallcells.png}
    \caption{A Gaussian Distribution Number Density Profile}
    \label{fig:Ensemble_Smallcells}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=2.5cm]{SameStatPic.png}
    \caption{Front views of a cube with eight smaller cells. The two views show two ways of picturing a fraction of vacancies, $f_v$ of 7/8 which give rise to the same Gaussian distribution statistically}
    \label{fig:SameStatPic}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=8cm]{VaryWidthandVacancies.png}
    \caption{Several Gaussian Distribution Number Density Profiles all with a number density of 1 atom per $V_{bold box}$}
    \label{fig:Ensemble_vary}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    %\includegraphics[height=4cm]{HomogeneousDen.png}
    \includegraphics[height=4cm]{Homogeneous_bold-box.png}
    \caption{A homogeneouse number density profile $n(\vec{r})$}
    \label{fig:homogen_denisty}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=5cm]{InclusionRadius.png}
    \caption{The Gaussians at each lattice point are of width gw. After a radius of few gw's the Gaussians go to zero and can be neglected.}
    \label{fig:InclusionRadius}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{AntitheticVariate.png}
    \caption{Antithetic variates reduce first order error in an average. Each point in the average is paired with another point from along the same line as the first, and at an equal, but opposite distance.}
    \label{fig:AntitheticVariate}
  \end{figure} 
Incorporating antithetic variates $-\vec{dr}$ for every $\vec{dr}$ equation ?? becomes:
\begin{displaymath}{n_i(\vec{r}_k, \vec{R}_j)=\sum_{NumPoints}\frac{1}{2}\frac{(1-f_v)\left[w_i(|\vec{r}-\vec{R_j}-\vec{dr}|) +w_i(|\vec{r}-\vec{R_j}+\vec{dr}|)\right]}{NumPoints}}\end{displaymath}   The process is repeated for all the other $\vec{R}_j$'s to get the total weighted densities at vector $\vec{r}_k$ due to all the Gaussians. 
\begin{displaymath}{n_i(\vec{r}_k)=\sum_j{n_i(\vec{r}_k, \vec{R}_j)}}\end{displaymath}
Then the entire process repeated for each vector $\vec{r}_k$ to get the total weighted densities $n_i(\vec{r})$ as a function of the position $\vec{r}$.

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{weight_functions.png}
    \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W2.png}
      \caption{A crossectional view of $w_2$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      \includegraphics[height=5cm]{W3.png}
      \caption{A crossectional view of $w_3$}
    \end{subfigure} 
    \caption{Cross-sectional views of the 3D weight functions. (a) $w_2$ is a spherical shell in 3D with soft edges. Weight functions $w_0$ and $w_1$ have a similar shape. (b) $w_3$ is a sphere with soft edges in 3D.}
    \label{fig:W0andW3}
    \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{GaussandW2_actual.png}
    \caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional view of $w_2$ centered at $\vec{r}'$ is shown in purple. Here, the weight function is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \caption{An alternative way of viewing Figure \ref{fig:GaussandW2_actual} where the weight function, shown by the purple dashed lines, is centered at $\vec{r}$  and fixed in place as $\vec{dr}$ varies randomly.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=3cm]{P_overlap.png}
    \caption{No energy is needed to place a sphere at a position where there is no overlap such as shown by the black dot at the center of the dotted region near the top. But it is not possible to place a sphere at a position where an overlap occurs.}
    \label{fig:p_overlap}
  \end{figure}

@@

--------------------------------------------------------------------------------
--------------------------------------------------------------------------------
 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{SimpleCell_Gaus.png}
    \caption{A 3D Gaussian Distribution}
    \label{fig:SimpleCell_Gaus}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{SimpleCell_Gaus.png}
    \caption{A homogeneouse number density profile $n(\vec{r})$}
    \label{fig:homogen_denisty}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{W0.png}
    \caption{A crossectional view of weight function $w_2$ which is a spherical shell with soft edges in 3D. Weight functions $w_0$ and $w_1$ have a similar shape.}
    \label{fig:W0}
    \end{figure}

 \begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{W3.png}
    \caption{A crossectional view of weight function $w_3$ which is a sphere with soft edges in 3D.}
    \label{fig:W3}
    \end{figure}

////////alpha and Xi vary with temp:
\begin{figure}[h!]
    \centering
    \includegraphics[height=4.7cm]{plot_alpha_vs_KbT.png}
    \caption{Shows how $\alpha$ varies with temperature}
    \label{fig:alpha_vs_T}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \includegraphics[height=4.7cm]{plot_xi_vs_KbT.png}
    \caption{Shows how $\Xi$ varies with temperature}
    \label{fig:xi_vs_T}
  \end{figure}

>>>>

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{plot_HardSphere_Potential.png}
    \caption{A Hard Sphere Potential is zero for $r>2R$, and infinity for $r\leq{2R}$ which is approximately 1.225 in this example.}
    \label{fig:HardSphere_potential}
  \end{figure}
\[{}\]
\[{}\]
\[{}\]
\[{}\]

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{LJ_Potential.png}
    \caption{Leonard-Jones Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{LJ_Potential_2part.png}
    \caption{Leanard-Jones Potential broken into two parts for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential_2parts}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{WCA_Potential.png}
    \caption{WCA Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:WCA_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
   % \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=3.5cm]{TwoSpheres.png}
    %\end{subfigure} 
    %\begin{subfigure}[b]{0.4\linewidth}
    %  \includegraphics[height=3.5cm]{2spheres.png}
    %\end{subfigure} 
    \caption{(Left) The WCA potential is a minimum at r=2R. 
             (Right) The WCA potential increases rapidly for $r<2R$.}
    \label{fig:TwoSpheres}
    \end{figure} 
%\[\]

@@

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=4.5cm]{plot_alpha_vs_KbT.png}
      %\includegraphics[height=5cm]{plot_alpha_vs_KbT.png}
      \caption{$\alpha$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=4.5cm]{plot_xi_vs_KbT.png}
      %\includegraphics[height=5cm]{plot_xi_vs_KbT.png}
      \caption{$\Xi$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \caption{These plots, generated with $\sigma=1$ and $\epsilon=1$, show how the parameters $\alpha$ and $\Xi$ vary with temperature. (a) $\alpha$ decreases with increasing temperature. (b) $\Xi$ rapidly increases for temperatures below $\frac{k_BT}{\epsilon}=52$ and then gradually decreases.}
    \label{fig:alphaXivsT}
    \end{figure}

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{Verf.png}
    %\includegraphics[height=5cm]{Verf.png}
    \caption{Error Function Potential $V_{erf}(r)$ at several temperatures with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ shown in black.}
    \label{fig:erf_potential}
  \end{figure}

@@

  \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=3.5cm]{PrimitiveCellLightBlue.png}
    \caption{The Primivitive Crystal Cell is shown by the shaded parallelpiped}
    \label{fig:primitivecell_firsttime}
  \end{figure}
%-------------------------------

@@

%For each particular temperature, the pressure of the liquid and the solid are the same at the point of transistion. 
\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=5cm]{P-T_Diagram.png}
    \caption{Conceptual Pressure-Temperature Phase Diagram}
    \label{fig:P-T_Diagram}
  \end{figure}
The pressure can be related to the Helmholtz free energy F, which is minimized for a system at fixed temperature, volume and number of particles as the entropy of the system and its surroundings is maximized. The negative of the partial derivative of the Helmholtz free energy with respect to volume V at a fixed temperature T and number of particles N equals the pressure. 
\begin{equation}{P=-\frac{\partial{F}}{\partial{V}}\bigg|_{T,N}}\end{equation}
\noindent Dividing both the Helmholtz free energy and the volume by the number of particles, the partial derivative of the Helmholtz free energy with respect to volume becomes the partial derivative of the Helmholtz free energy per atom with respect to the inverse number density. \begin{equation}{P=-\frac{\partial{\frac{F}{N}}}{\partial{\frac{V}{N}}}\bigg|_{T,N} = -\frac{\partial{f}}{\partial{\frac{1}{n}}}\bigg|_{T,N}}\end{equation} Thus, the pressure corresponds to the slope of the curve on a plot of the Helmholtz free energy per atom versus the inverse density at fixed temperature.

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{MDTC.png}
    \caption{Identifying densities at the solid-liquid transition using Maxwell's Double Tangent Construction}
    \label{fig:MaxwellDT}
  \end{figure}

@@

The pressure at the transistion point can be obtained from the point of intersection that occurs when the Gibbs free energy per atom is plotted against the pressure for both the liquid and the solid at fixed temperature, as shown in Figure \ref{fig:GibbsvsP}. These curves are constructed from the slope and cooresponding y-intercept data collected from lines tangent along the curves on the the Helmholtz free energy per atom verses inverse density plots for both the liquid and the solid. 
\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{MDTC-2.png}
    \caption{Pressure is found at point of intersection which occurs when $g_L=g_S$}
    \label{fig:GibbsvsP}
  \end{figure}
%CURVE FITTING! - put in methods/analysis

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{MDTC-3.png}
    \caption{The liquid and solid densities at the point of transistion are found from a plot of pressure vs inverse denisty for both the liquid and the solid.}
    \label{fig:Pvsinvn}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{T-n_Diagram.png}
    \caption{Conceptual Temperature-Density Phase Diagram used to identify the number densities of the liquid and the solid during a phase transistion. The gray region is where the liquid and the solid coexist, and are therefore not pure states.}
    \label{fig:T-n_Diagram}
  \end{figure} 
%One way of implementing this practically is to determine what the Helmholtz free energy would be for both the liquid and solid phases at a particular temperature and density. Whichever phase has the lower Helmholtz free energy will be the phase that the substance will be in. 
%\[\]
\[\]
IC. Classical Density Functional Theory (cDFT)

@@

  \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4.5cm]{PrimitiveCellLightBlue.png}
    \caption{The Primivitive Crystal Cell is shown by the shaded parallelpiped}
    \label{fig:primitivecell}
  \end{figure}

  \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4.5cm]{Simple_Cell.png}
    \caption{A Simplified Crystal Cell}
    \label{fig:simplecell}
  \end{figure}

@@

  \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=2.5cm]{Ensemble_Gaussian.png}
    \caption{A Gaussian Distribution Number Density Profile}
    \label{fig:Ensemble_Gaus}
  \end{figure}

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{Gaussian_Plot.png}
    \caption{A 2D Gaussian Distribution of width 2$\sigma$}
    \label{fig:Gaus_plot}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=2.5cm]{Ensemble_Smallcells.png}
    \caption{A Gaussian Distribution Number Density Profile}
    \label{fig:Ensemble_Smallcells}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=2.5cm]{SameStatPic.png}
    \caption{Front views of a cube with eight smaller cells. The two views show two ways of picturing a fraction of vacancies, $f_v$ of 7/8 which give rise to the same Gaussian distribution statistically}
    \label{fig:SameStatPic}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=8cm]{VaryWidthandVacancies.png}
    \caption{Several Gaussian Distribution Number Density Profiles all with a number density of 1 atom per $V_{bold box}$}
    \label{fig:Ensemble_vary}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    %\includegraphics[height=4cm]{HomogeneousDen.png}
    % FIXME \includegraphics[height=4cm]{Homogeneous_bold-box.png}
    \caption{A homogeneouse number density profile $n(\vec{r})$}
    \label{fig:homogen_denisty}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=5cm]{InclusionRadius.png}
    \caption{The Gaussians at each lattice point are of width gw. After a radius of few gw's the Gaussians go to zero and can be neglected.}
    \label{fig:InclusionRadius}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{AntitheticVariate.png}
    \caption{Antithetic variates reduce first order error in an average. Each point in the average is paired with another point from along the same line as the first, and at an equal, but opposite distance.}
    \label{fig:AntitheticVariate}
  \end{figure} 
Incorporating antithetic variates $-\vec{dr}$ for every $\vec{dr}$ equation ?? becomes:
\begin{displaymath}{n_i(\vec{r}_k, \vec{R}_j)=\sum_{NumPoints}\frac{1}{2}\frac{(1-f_v)\left[w_i(|\vec{r}-\vec{R_j}-\vec{dr}|) +w_i(|\vec{r}-\vec{R_j}+\vec{dr}|)\right]}{NumPoints}}\end{displaymath}   The process is repeated for all the other $\vec{R}_j$'s to get the total weighted densities at vector $\vec{r}_k$ due to all the Gaussians. 
\begin{displaymath}{n_i(\vec{r}_k)=\sum_j{n_i(\vec{r}_k, \vec{R}_j)}}\end{displaymath}
Then the entire process repeated for each vector $\vec{r}_k$ to get the total weighted densities $n_i(\vec{r})$ as a function of the position $\vec{r}$.

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{weight_functions.png}
    \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME % FIXME \includegraphics[height=5cm]{W2.png}
      \caption{A crossectional view of $w_2$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=5cm]{W3.png}
      \caption{A crossectional view of $w_3$}
    \end{subfigure} 
    \caption{Cross-sectional views of the 3D weight functions. (a) $w_2$ is a spherical shell in 3D with soft edges. Weight functions $w_0$ and $w_1$ have a similar shape. (b) $w_3$ is a sphere with soft edges in 3D.}
    \label{fig:W0andW3}
    \end{figure}

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{GaussandW2_actual.png}
    \caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional view of $w_2$ centered at $\vec{r}'$ is shown in purple. Here, the weight function is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \caption{An alternative way of viewing Figure \ref{fig:GaussandW2_actual} where the weight function, shown by the purple dashed lines, is centered at $\vec{r}$  and fixed in place as $\vec{dr}$ varies randomly.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=3cm]{P_overlap.png}
    \caption{No energy is needed to place a sphere at a position where there is no overlap such as shown by the black dot at the center of the dotted region near the top. But it is not possible to place a sphere at a position where an overlap occurs.}
    \label{fig:p_overlap}
  \end{figure}

@@

--------------------------------------------------------------------------------
--------------------------------------------------------------------------------
 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{SimpleCell_Gaus.png}
    \caption{A 3D Gaussian Distribution}
    \label{fig:SimpleCell_Gaus}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{SimpleCell_Gaus.png}
    \caption{A homogeneouse number density profile $n(\vec{r})$}
    \label{fig:homogen_denisty}
  \end{figure}

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{W0.png}
    \caption{A crossectional view of weight function $w_2$ which is a spherical shell with soft edges in 3D. Weight functions $w_0$ and $w_1$ have a similar shape.}
    \label{fig:W0}
    \end{figure}

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4cm]{W3.png}
    \caption{A crossectional view of weight function $w_3$ which is a sphere with soft edges in 3D.}
    \label{fig:W3}
    \end{figure}

////////alpha and Xi vary with temp:
\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4.7cm]{plot_alpha_vs_KbT.png}
    \caption{Shows how $\alpha$ varies with temperature}
    \label{fig:alpha_vs_T}
  \end{figure}

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=4.7cm]{plot_xi_vs_KbT.png}
    \caption{Shows how $\Xi$ varies with temperature}
    \label{fig:xi_vs_T}
  \end{figure}
